hbm_paper_results

### 2024-02-03 paper_main_results.Rmd
fixing big sex-differences violin plot and adding sig values

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")
```
```{r}
source("./cubic_scripts/R_scripts/stats_tests.R")
# devtools::source_url("https://raw.githubusercontent.com/BGDlab/combat-biovar/main/cubic_scripts/R_scripts/stats_tests.R")
```

@@

#plotting info from dk atlas
dk.parc <- dk_nomed$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()

#write out new dk atlas w/o medial wall
dk_nomed <- dk
dk_nomed$data <- dk_nomed$data %>%
  dplyr::filter(!is.na(region) & region !="corpus callosum")
```

@@

Little plot
```{r}
#get means w/in feature 
mean.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno, pheno_abs.diff.list) %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))
```

@@

Plot errors for global phenotypes
```{r}
global_abs.diffs <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", vol_list_global)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff")

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Magnitude Centile Error", x = "Phenotype") +
  theme(plot.title = element_text(size=12)) +
  ggtitle("Magnitude error in centile scores")
ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

@@

med.diffs.plot <- ggplot(med.diffs.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_centile_abs.diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5)) #
med.diffs.plot
```

@@

med.diffs.plot.global <- ggplot(med.diffs.plot.global.df) +
  geom_rect(data = tp, fill="gray", xmin = -Inf,xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.4) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_centile_abs.diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5))
med.diffs.plot.global
```

Combine plots - need to keep playing around to make the spacing pretty when it saves out
```{r}
p_diff <- ggarrange(
  med.diffs.plot.global, med.diffs.plot,
  ncol=2, nrow=1, 
  widths = c(1, 3.1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

p_diff_annotate <- annotate_figure(p_diff)
p_diff_annotate
```

@@

```{r}
plt.df <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", pheno_list)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100,
         pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)))
```
```{r}
custom_strip <- strip_themed(
     text_x = elem_list_text(angle = 90, color="black"),
     background_x=element_blank()
)

big_violin_plt <- plt.df %>% 
  ggplot() +
  geom_violin(aes(x=pheno, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines")) +
  facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x", switch="x", strip = custom_strip) +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")

ggsave("figs/big_sex_violin_plt.jpeg", big_violin_plt, width=12, height=6, units="in")
```
*need to add stats tests*
```{r}
regional_violin_plt <- plt.df %>%
  dplyr::filter(!pheno %in% vol_list_global) %>%
  ggplot() +
  geom_violin(aes(x=pheno, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines"), legend.position="bottom") +
  facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x") +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
```

```{r}
global_violin_sex_plt <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels | dataset == "cf.lm"
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100) %>%
  ggplot(aes(x=pheno, y=diff, fill=sex)) +
  geom_rain(likert= TRUE,
            point.args=list(color=NA, fill=NA),
 boxplot.args.pos = list(position = ggpp::position_dodgenudge(x = -.07), width = .3),
 violin.args = list(color=NA, alpha = .7))+
  theme_linedraw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="bottom") +
  labs(y="Centile Error", x = "Brain Feature") +
  facet_wrap(~dataset)
```

```{r}
diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", pheno_list)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100,
         pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  # scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  # scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Centile Error", x = "Brain Feature") +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), ggh4x.axis.nesttext.x = element_text(angle = 45)) +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
```

@@

wmv_centile_fan <- ggplot(wmv.df) +
  geom_jitter(data = ukb_cn_df, aes(x=ukb_cn_df$age_years, y=ukb_cn_df$WMV), alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  #geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('ukb-CN-simsites'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "solid"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #scale_color_manual(values = c('ukb-CN-simsites'= "black", cf.gam = "#E84617", cf.gamlss = "#17E846", cf.lm = "purple")) +
  scale_color_manual(values = c('ukb-CN-simsites'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = 0.35, size=2) +
  xlab("Age (yrs)") + ylab("Volume (mm3)") +
  theme_linedraw(base_size = 11) +
  theme(plot.title = element_text(size=12)) +
  labs(title="White matter volume brain charts")
wmv_centile_fan
```
toy brain chart for figs

@@

```{r}
fig_1 <- ggarrange(
  wmv_centile_fan, global_cent_errs_plot,
  ncol=2, nrow=1, 
  widths = c(1.75, 1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom",
  labels="auto"
  )

fig_1_annotate <- annotate_figure(fig_1, top = text_grob("Figure 1. Choice of ComBat configuration can induce errors in brain feature centile scores",
               color = "black", hjust = 0, x = 0))
fig_1_annotate
ggsave("figs/figure_1.jpeg", fig_1_annotate, width=11, height=5)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, ggh4x)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")
```
```{r}
source("./cubic_scripts/R_scripts/stats_tests.R")
# devtools::source_url("https://raw.githubusercontent.com/BGDlab/combat-biovar/main/cubic_scripts/R_scripts/stats_tests.R")
```

@@

#write out new dk atlas w/o medial wall
dk_nomed <- dk
dk_nomed$data <- dk_nomed$data %>%
  dplyr::filter(!is.na(region) & region !="corpus callosum")
#plotting info from dk atlas
dk.parc <- dk_nomed$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
```

@@

Little plot
```{r}
#get means w/in feature 
mean.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno_abs.diff.list) %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))
```

@@

Plot errors for global phenotypes

get stat results for global phenos:
```{r, message=FALSE}
full_cent_res <- centile.t.tests.full_result(diffs.df, feature_list=pheno_abs.diff.list)
full_cent_res %>%
  dplyr::filter(pheno %in% vol_list_global) %>%
  dplyr::filter(!grepl('_refA', comp))
```

all significant

```{r}
global_abs.diffs <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", vol_list_global)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff")

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #WMV
geom_signif(y_position = c(29, 30.5, 4), xmin = c(0.7, 0.7, 1), 
              xmax = c(1, 1.3, 1.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #GMV
  geom_signif(y_position = c(30, 31.5, 3), xmin = c(1.7, 1.7, 2), 
              xmax = c(2, 2.3, 2.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #sGMV
  geom_signif(y_position = c(28, 29.5, 2.8), xmin = c(2.7, 2.7, 3), 
              xmax = c(3, 3.3, 3.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #Ventricles
  geom_signif(y_position = c(24, 25.5, 7.5), xmin = c(3.7, 3.7, 4), 
              xmax = c(4, 4.3, 4.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  labs(y="Magnitude Centile Error", x = "Phenotype") +
  theme(plot.title = element_text(size=12)) +
  ggtitle("Magnitude error in centile scores")
global_cent_errs_plot
# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

@@

med.diffs.plot <- ggplot(med.diffs.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_centile_abs.diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5)) #
# med.diffs.plot
```

@@

med.diffs.plot.global <- ggplot(med.diffs.plot.global.df) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_centile_abs.diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5))
# med.diffs.plot.global
```

Combine plots - need to keep playing around to make the spacing pretty when it saves out
```{r}
p_diff <- ggarrange(
  med.diffs.plot.global, med.diffs.plot,
  ncol=2, nrow=1, 
  widths = c(.95, 3.1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

p_diff_annotate <- annotate_figure(p_diff, top = text_grob("Magnitude Centile Errors", color = "black", hjust = 0, x = 0.06))
p_diff_annotate
```

@@

```{r}
plt.df <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", pheno_list)) %>% #select centile errors only
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100,
         pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_), ordered=TRUE, levels=c("Global Volume", "Regional Volume", "Regional SA", "Regional CT"))) %>%
    mutate(pheno = factor(pheno, ordered=TRUE, levels=c(vol_list_global, vol_list_regions, sa_list, ct_list)))#sort w/in pheno_cat
```

stat test re-do w wilcox 
```{r}
stat.test <- plt.df %>%
  group_by(dataset, pheno) %>%
  wilcox_test(diff ~ sex) %>%
  adjust_pvalue(method = "fdr") %>%
  add_significance("p.adj")
```
```{r}
stat.test2 <- stat.test %>%
  add_xy_position(x = "pheno", dodge = 0.8, fun="max") %>%
  mutate(p.adj.signif = ifelse(p.adj.signif == "ns", "ns", "*"))
stat.test2 %>%
  dplyr::filter(phen_cat=="")
```

```{r}
# custom_strip <- strip_themed(
#      text_x = elem_list_text(angle = 90, color="black"),
#      background_x=element_blank()
# )

dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

big_violin_plt <- plt.df %>%
  ggplot(aes(x=pheno, y=diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  # geom_violin(aes(fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  stat_pvalue_manual(stat.test2, label = "p.adj.signif", label.size = 1, tip.length = 0, hide.ns = FALSE, remove.bracket = TRUE) +
  # facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x", switch="x", strip = custom_strip) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), ggh4x.axis.nesttext.x = element_text(angle = 45)) +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
big_violin_plt
ggsave("figs/big_sex_violin_plt.jpeg", big_violin_plt, width=12, height=6, units="in")
```

*need to add stats tests*
```{r}
regional_violin_plt <- plt.df %>%
  dplyr::filter(!pheno %in% vol_list_global) %>%
  ggplot() +
  geom_violin(aes(x=pheno, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines"), legend.position="bottom") +
  facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x") +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
```

```{r}
global_violin_sex_plt <- diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels | dataset == "cf.lm"
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100) %>%
  ggplot(aes(x=pheno, y=diff, fill=sex)) +
  geom_rain(likert= TRUE,
            point.args=list(color=NA, fill=NA),
 boxplot.args.pos = list(position = ggpp::position_dodgenudge(x = -.07), width = .3),
 violin.args = list(color=NA, alpha = .7))+
  theme_linedraw(base_size = 11) +
  stat_compare_means(method = "wilcox.test", label="p.signif") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="bottom") +
  labs(y="Centile Error", x = "Brain Feature") +
  facet_wrap(~dataset)
global_violin_sex_plt
```

```{r}
diffs.df %>%
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("diff_", pheno_list)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         diff = diff*100,
         pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>% #for visuals
  ggplot(aes(y=diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  # scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  # scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Centile Error", x = "Brain Feature") +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), ggh4x.axis.nesttext.x = element_text(angle = 45)) +
  ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
```

@@

wmv_centile_fan <- ggplot(wmv.df) +
  geom_jitter(data = ukb_cn_df, aes(x=ukb_cn_df$age_years, y=ukb_cn_df$WMV), alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  #geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('ukb-CN-simsites'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "solid"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c('ukb-CN-simsites'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = 0.35, size=2) +
  xlab("Age (yrs)") + ylab("Volume (mm3)") +
  theme_linedraw(base_size = 11) +
  theme(plot.title = element_text(size=12), legend.position="bottom") +
  labs(title="White matter volume brain charts")
wmv_centile_fan
```
toy brain chart for figs

@@

```{r}
fig_1 <- ggarrange(
  wmv_centile_fan,
  ggarrange(global_cent_errs_plot, p_diff_annotate, ncol=1, nrow=2, heights = c(1.2, 2), common.legend = FALSE, labels=c("B", "C")),
  ncol=2, nrow=1, 
  labels=c("A", NA),
  widths=c(1.1, 1)
  #hjust=0.01,
  # align = "hv"
  )

fig_1_annotate <- annotate_figure(fig_1, top = text_grob("Figure 1. Choice of ComBat configuration can induce errors in brain feature centile scores",
               color = "black", hjust = 0, x = 0))
fig_1_annotate
ggsave("figs/figure_1.jpeg", fig_1_annotate, width=11, height=7, units="in")
```
